### 2015-01-10 mcmc.tex
notes to self; tweaks

% to-do
% -----
% - perhaps re-order to m-h, convergence, reporting results, other methods ??
% - where to put comments about how to structure code ln_likelihood(pars, data, I) and ln_prior(pars, I)
% - need to mention case where there is an MC integral INSIDE the likelihood function
% - need to mention testing the likelihood function
% - send to friendlies for comments
%   - Lang
%   - Rix
%   - Bovy
%   - Brewer
%   - Hill
% - post on arXiv

@@

The only significant technical details for importance sampling are the
following:
The approximate function must have the same (or greater) support as
the true function, and the method degrades in efficiency as the two
functions diverge.
If the ratio of the true function to the approximate function is to be
used as a probability for rejection of samples, then the true function
must be greater than or equal to the approximate function everywhere!

@@

>>>>

% to-do
% -----
% - mention JAGS and STAN in methods section
% - perhaps re-order to m-h, convergence, reporting results, other methods ??
% - where to put comments about how to structure code ln_likelihood(pars, data, I) and ln_prior(pars, I)
% - need to mention case where there is an MC integral INSIDE the likelihood function
% - need to mention testing the likelihood function
% - send to friendlies for comments
%   - Lang
%   - Rix
%   - Bovy
%   - Brewer
%   - Hill
% - post on arXiv

@@

Two of the significant technical details for importance sampling are the
following:
The approximate function must have the same (or greater) support as
the true function, and the method degrades in efficiency as the two
functions diverge.
If the ratio of the true function to the approximate function is to be
used as a probability for rejection of samples, then the true function
must be greater than or equal to the approximate function everywhere!

@@

\paragraph{Data augmentation:}
...HOGG?
